### 2018-03-17 paper/4-build.tex
Final tweaks to S4

A build system that uses verifying traces needs to persistently maintain a set
of traces. After computing a fresh value we add its \hs{Trace}~\hs{k}~\hs{v} to
the set. Therefore the information stored by a build system that verifies
traces can be stored as a list or set~--~we chose \hs{[Trace}~\hs{k}~\hs{v]}
for simplicity. In practice, different build systems can optimise the data
structures used by traces for their specific use cases, which we discuss
in~\S\ref{sec-smart-traces}.

@@

We have a list of traces, plus a \hs{Map} from the hash to the actual contents. Checking a trace is the same as before, but if the result is the only thing that is different we can simply retrieve a fresh result from \hs{contents} \emph{without} recomputing it. We split the traces and contents as in cloud interactions to a remote server the checking system may have to examine many traces/hashes, but only at most one complete file.

>>>>

A build system that uses verifying traces needs to persistently maintain a set
of traces. After computing a fresh value we add its \hs{Trace}~\hs{k}~\hs{v} to
the set. Therefore the information stored by a build system that verifies
traces can be modelled as a list or set~--~we chose \hs{[Trace}~\hs{k}~\hs{v]}
for simplicity. In practice, different build systems can optimise the data
structures used by traces for their specific use cases, which we discuss
in~\S\ref{sec-smart-traces}.

@@

We have a list of traces, plus a \hs{Map} from the hash to the actual contents. Checking a trace is the same as before, but if the result is the only thing that is different we can simply retrieve a fresh result from \hs{contents} \emph{without} recomputing it. We split the traces and contents because in cloud interactions to a remote server the checking system may have to examine many traces/hashes, but only retrieve at most one complete file per key.
